---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# model.comp

<!-- badges: start -->
<!-- badges: end -->

The goal of model.comp is to compare the performance of some fitted models on the given data.
(Note: currently, only supports returning the fitted values, and only supports a logistic regression model. This will be expanded on in the future.)

The package website can be found here: https://hantonita.github.io/model.comp/

## Installation

This package is not on CRAN yet so the best way to install it is using the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hantonita/model.comp")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(model.comp)
(compare_models(data = gapminder::gapminder, eqn = "lifeExp ~ gdpPercap", models = c('logreg')))
```


## Code of Conduct

Please note that the model.comp project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


----------------------------------------------------------------

## Exercise 1.1:
To create this R package, the following steps were used:
```
library(devtools)
usethis::create_package('~Documents/model.comp')
``` 
to make an R package

```
library(devtools)
usethis::use_git()
``` 
to ensure that the project is using git. Then I created a repository on github with the same name, and used the shell opened from my R project to push the existing repository to github.

```
library(devtools)
usethis::use_r('compare')
```
to create the `compare.R` file to hold my `compare` function.

I then edited the `DESCRIPTION` file, adding a title and the author information, and using `usethis::use_mit_license()` to add a license to my package.

Package dependencies were added to the `DESCRIPTION` file using `usethis::use_package(<package name>)`, and a vignette was created using `usethis::use_vignette()`.

Documentation was finally updated using `devtools::document()`

