---
title: "Getting started: model.comp "
author: "Hanna Frank"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started: model.comp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `model.comp` helps compare performance measures of models fitted to given data. To get started, load the package as such:

```{r}
library(model.comp)
```

Then call the `compare_models()` function, specifying your input `data`, the `models` you want to fit, given as a list or vector, the `outputs` you would like to compare, also given as a list or vector, and your `eqn` - the format of the models you would like to fit.

Currently, the models supported are:  

- `logreg`: logistic regression

The supported outputs are: 

- `fitted_values`: the values predicted using the fitted model for the given dataset.

An example is given below for the `logreg` model, using the `gapminder` dataset as test data:

```{r}
logreg_output <- compare_models(data = gapminder::gapminder, eqn = "lifeExp ~ gdpPercap", models = c('logreg'))
```

